---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--when changes where made run devtools::build_readme() in 01_start.R -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ClusterApp

<!-- badges: start -->
<!-- badges: end -->

The `ClusterApp` is a Shiny App developed for the easy and straightforward analysis of GPS collared individuals to identify clusters of visits.

Our aim is to provide a streamlined method to apply cluster analyses to GPS data without the need to have prior knowledge regarding the use of geographical or statistical software. To facilitate this, we created the “ClusterAnalysis” Shiny R application (version 1.0). We expect the app to contribute to the continuity of methods regarding data collection (decrease observer biases), straightforward usage for field personnel, and reliable data management.

The app was built using the `golem` framework.

## Installation

You can install the development version of ClusterApp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JohannaMz/ClusterApp")
```


## Run the app 

To launch the `ClusterApp`, load the library and type the following code into the R console. 


```{r run}
library(ClusterApp)
ClusterApp::run_app()
```

## How to use the app 

maybe there will be a guided tutorial with the bear and wolf data. check out the preprint [here](url)

## Help 

If you encounter a bug, please submit an issue on github? For general questions and feedback, contact [Johanna Märtz](johanna@maertz.eu).

##Citation 

```{r citation}
citation("ClusterApp")
```

