---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"inst/app/www/favicon.png" style=\"float: right;width: 150px;\"/>')
   });
</script>

# ClusterApp

<!-- badges: start -->
<!-- badges: end -->

The goal of ClusterApp is a Shiny application to guide and streamline cluster studies based on GPS data.

## Installation

You can install the development version of ClusterApp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JohannaMz/ClusterApp")
```

The app can then be started by the command:

``` r
library(ClusterApp)
ClusterApp::run_app()
```

## Tutorial 

A tutorial for the usage of the app can be accessed [here](https://github.com/JohannaMz/ClusterApp/ClusterApp_tutorial.pdf). 


## Getting help

If you encounter a bug, please [submit an issue](https://github.com/JohannaMz/ClusterApp/issues). For more general questions and suggestions, contact Johanna Märtz (johanna@maertz.eu).

## Citation

```{r citation}
citation("ClusterApp")
```
